\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-27 sections/introduction.tex
Update introduction
1. Delete paragraph about metagenomics and metatranscriptomics
2. Add tex root
3. Fix indentation

@@

    We will further collect metagenomic data (whole genome shotgun sequence data), metatranscriptomic data (mRNA sequence data) and metabolomic data (metabolite profile from mass spectroscopy) and incorporate these into the database in the next phase of the project.
    This addition would enable us to obtain a mechanistic perspective of the dynamics in a microbial community.
    The heterogeneous multi-omic data-sets will open new avenues and exciting approaches for generating new knowledge.
    This data can be leveraged to provide insights into previously unknown microbial ecological interaction network dynamics upon integration into the database.
    We will also make use of \ac{comets} simulations to predict interactions in microbial communities and to design synthetic communities.

>>>>

%!TEX root = ../main.tex

@@
